
# Exploratory Analysis


<!-- <iframe width = "700" height = "500" src="plots/plotly_cluster.html"></iframe> -->

## PCA and Clustering

```{r}
#| echo: false
#| message: false
#| warning: false
load('PCA_Data.RData')
library(plotly)
library(factoextra)

plot_ly(
  data = cluster_data,
  x = ~PC1,
  y = ~PC2,
  type = 'scatter',
  mode = 'markers',
  color = ~factor(kmeans_cluster_k),
  colors = c("#797d97", "#cac7b9","#eeaa46", "#4a2329", "#e15b4f"),
  text = ~paste("ID:", survey_data_2022_pca$id), 
  hoverinfo = 'text',
  marker = list(size = 8, opacity = 1)
) %>%
  layout(
    title = list(
      text = "K-means Clustering on PCA Data",
      x = 0.5,                      
      xanchor = "center"
    ),
    xaxis = list(title = "PC1"),
    yaxis = list(title = "PC2"),
    legend = list(title = list(text = "Cluster"))
  )

<<<<<<< Updated upstream
```

=======

```
## Survey Question Loading Plot
>>>>>>> Stashed changes
```{r}
#| echo: false
#| message: false
#| warning: false
<<<<<<< Updated upstream
load('bar_graph_data.RData')

library(ggpubr)
library(haven)
library(tidyverse)
library(ggplot2)
library(dplyr)
library(forcats)
library(viridis)

plt1<-ggplot(survey_data_2022_cleaner,aes(x=Year,fill=Q5_1))+
  geom_bar()+
  scale_fill_manual(values = c(
     "Extremely Important"  = "#7b3294",
     "Very Important"       = "#984ea3",
     "Somewhat Important"   = "#a05260", 
     "Not Too Important"    = "#905d5d",
     "Not At All Important" = "#984ea3",
     "No Response" = 'lightgrey'))+
  facet_grid(~MUSEUMTYPE)+
  theme_minimal()+labs(title="How important to you is it that your museum currently serves in the following capacity:The museum regularly acquires artwork?")


plt2<-ggplot(survey_data_2020_cleaner,aes(x=Year,fill=Q7_1))+
  geom_bar()+
   scale_fill_manual(values = c(
     "Extremely Important"  = "#7b3294",
     "Very Important"       = "#984ea3",
     "Somewhat Important"   = "#a05260", 
     "Not Too Important"    = "#905d5d",
     "Not At All Important" = "#984ea3",
     "No Response" = 'lightgrey'))+ 

  facet_grid(~MUSEUMTYPE)+
  theme_minimal()+labs(title="How important to you is it that your museum currently serves in the following capacity:The museum regularly acquires artwork?")

plt3<-ggarrange(plt2,plt1,ncol = 2, nrow = 2)

print(plt3)
```

```{r}
#| echo: false
#| message: false
#| warning: false
plt4<-ggplot(survey_data_2022_cleaner,aes(x=Year,fill=Q5_2))+
  geom_bar()+
  scale_fill_manual(values = c(
     "Extremely Important"  = "#7b3294",
     "Very Important"       = "#984ea3",
     "Somewhat Important"   = "#a05260", 
     "Not Too Important"    = "#905d5d",
     "Not At All Important" = "#984ea3",
     "No Response" = 'lightgrey'))+
  facet_grid(~MUSEUMTYPE)+
  theme_minimal() + labs(title="How important to you is it that your museum currently displays artwork from its permanent collections")


plt5<-ggplot(survey_data_2020_cleaner,aes(x=Year,fill=Q7_2))+
  geom_bar()+
   scale_fill_manual(values = c(
     "Extremely Important"  = "#7b3294",
     "Very Important"       = "#984ea3",
     "Somewhat Important"   = "#a05260", 
     "Not Too Important"    = "#905d5d",
     "Not At All Important" = "#984ea3",
     "No Response" = 'lightgrey'))+ #
  facet_grid(~MUSEUMTYPE)+
  theme_minimal()+labs(title="How important to you is it that your museum currently displays artwork from its permanent collections")

plt6<-ggarrange(plt4,plt5,ncol = 2, nrow = 2)
print(plt6)

```

```{r}
#| echo: false
#| message: false
#| warning: false
plt7<-ggplot(survey_data_2022_cleaner,aes(x=Year,fill=Q6_1))+
  geom_bar()+
  scale_fill_manual(values = c(
     "Extremely Important"  = "#7b3294",
     "Very Important"       = "#984ea3",
     "Somewhat Important"   = "#a05260", 
     "Not Too Important"    = "#905d5d",
     "Not At All Important" = "#984ea3",
     "No Response" = 'lightgrey'))+
  facet_grid(~MUSEUMTYPE)+
  theme_minimal()+labs(title="How important to you is it that your museum will serve in the following capacity in five years: regularly acquire artwork?")


plt8<-ggplot(survey_data_2020_cleaner,aes(x=Year,fill=Q8_1))+
  geom_bar()+
   scale_fill_manual(values = c(
     "Extremely Important"  = "#7b3294",
     "Very Important"       = "#984ea3",
     "Somewhat Important"   = "#a05260", 
     "Not Too Important"    = "#905d5d",
     "Not At All Important" = "#984ea3",
     "No Response" = 'lightgrey'))+ #
  facet_grid(~MUSEUMTYPE)+
  theme_minimal()+labs(title="How important to you is it that your museum will serve in the following capacity in five years: regularly acquire artwork?")

plt9<-ggarrange(plt7,plt8,ncol = 2, nrow = 2)
print(plt9)
```

```{r}
#| echo: false
#| message: false
#| warning: false
plt10<-ggplot(survey_data_2022_cleaner,aes(x=Year,fill=Q6_2))+
  geom_bar()+
  scale_fill_manual(values = c(
     "Extremely Important"  = "#7b3294",
     "Very Important"       = "#984ea3",
     "Somewhat Important"   = "#a05260", 
     "Not Too Important"    = "#905d5d",
     "Not At All Important" = "#984ea3",
     "No Response" = 'lightgrey'))+
  facet_grid(~MUSEUMTYPE)+
  theme_minimal()+labs(title="How important to you is it that your museum will serve in the following capacity in five years:display artwork from its permanent collections?")


plt11<-ggplot(survey_data_2020_cleaner,aes(x=Year,fill=Q8_2))+
  geom_bar()+
   scale_fill_manual(values = c(
     "Extremely Important"  = "#7b3294",
     "Very Important"       = "#984ea3",
     "Somewhat Important"   = "#a05260", 
     "Not Too Important"    = "#905d5d",
     "Not At All Important" = "#984ea3",
     "No Response" = 'lightgrey'))+ #
  facet_grid(~MUSEUMTYPE)+
  theme_minimal()+labs(title="How important to you is it that your museum will serve in the following capacity in five years:display artwork from its permanent collections?")

plt12<-ggarrange(plt10,plt11,ncol = 2, nrow = 2)
print(plt12)

```

```{r}
#| echo: false
#| message: false
#| warning: false
plt13<-ggplot(survey_data_2022_cleaner,aes(x=Year,fill=Q6_4))+
  geom_bar()+
  scale_fill_manual(values = c(
     "Extremely Important"  = "#7b3294",
     "Very Important"       = "#984ea3",
     "Somewhat Important"   = "#a05260", 
     "Not Too Important"    = "#905d5d",
     "Not At All Important" = "#984ea3",
     "No Response" = 'lightgrey'))+
  facet_grid(~MUSEUMTYPE)+
  theme_minimal()+labs(title="How important to you is it that your museum will serve in the following capacity in five years: The museum ensures the conservation of its collections for the long-term future")


plt14<-ggplot(survey_data_2020_cleaner,aes(x=Year,fill=Q8_4))+
  geom_bar()+
   scale_fill_manual(values = c(
     "Extremely Important"  = "#7b3294",
     "Very Important"       = "#984ea3",
     "Somewhat Important"   = "#a05260", 
     "Not Too Important"    = "#905d5d",
     "Not At All Important" = "#984ea3",
     "No Response" = 'lightgrey'))+ #
  facet_grid(~MUSEUMTYPE)+
  theme_minimal()+labs(title="How important to you is it that your museum will serve in the following capacity in five years: The museum ensures the conservation of its collections for the long-term future")

plt15<-ggarrange(plt13,plt14,ncol = 2, nrow = 2)
print(plt15)

```

```{r}
#| echo: false
#| message: false
#| warning: false
plt16<-ggplot(survey_data_2022_cleaner,aes(x=Year,fill=Q8_9))+
  geom_bar()+
  scale_fill_manual(values = c(
     "Extremely Important"  = "#7b3294",
     "Very Important"       = "#984ea3",
     "Somewhat Important"   = "#a05260", 
     "Not Too Important"    = "#905d5d",
     "Not At All Important" = "#984ea3",
     "No Response" = 'lightgrey'))+
  facet_grid(~MUSEUMTYPE)+
  theme_minimal()+labs(title="How much of a priority do you think each of the following equity, diversity, and inclusion strategies are in the art museum sector as a whole?:Increasing the diversity of staff in senior management positions")


plt17<-ggplot(survey_data_2020_cleaner,aes(x=Year,fill=Q10_9))+
  geom_bar()+
   scale_fill_manual(values = c(
     "Extremely Important"  = "#7b3294",
     "Very Important"       = "#984ea3",
     "Somewhat Important"   = "#a05260", 
     "Not Too Important"    = "#905d5d",
     "Not At All Important" = "#984ea3",
     "No Response" = 'lightgrey'))+ #
  facet_grid(~MUSEUMTYPE)+
  theme_minimal()+labs(title="How much of a priority do you think each of the following equity, diversity, and inclusion strategies are in the art museum sector as a whole?:Increasing the diversity of staff in senior management positions")

plt18<-ggarrange(plt16,plt17,ncol = 2, nrow = 2)
print(plt18)
```

```{r}
#| echo: false
#| message: false
#| warning: false
plt19<-ggplot(survey_data_2022_cleaner,aes(x=Year,fill=Q8_11))+
  geom_bar()+
  scale_fill_manual(values = c(
     "Extremely Important"  = "#7b3294",
     "Very Important"       = "#984ea3",
     "Somewhat Important"   = "#a05260", 
     "Not Too Important"    = "#905d5d",
     "Not At All Important" = "#984ea3",
     "No Response" = 'lightgrey'))+
  facet_grid(~MUSEUMTYPE)+
  theme_minimal()+labs(title="How much of a priority do you think each of the following equity, diversity, and inclusion strategies are in the art museum sector as a whole?:Increasing the diversity of museum volunteers")


plt20<-ggplot(survey_data_2020_cleaner,aes(x=Year,fill=Q10_10))+
  geom_bar()+
   scale_fill_manual(values = c(
     "Extremely Important"  = "#7b3294",
     "Very Important"       = "#984ea3",
     "Somewhat Important"   = "#a05260", 
     "Not Too Important"    = "#905d5d",
     "Not At All Important" = "#984ea3",
     "No Response" = 'lightgrey'))+ #
  facet_grid(~MUSEUMTYPE)+
  theme_minimal()+labs(title="How much of a priority do you think each of the following equity, diversity, and inclusion strategies are in the art museum sector as a whole?:Increasing the diversity of museum volunteers")

plt21<-ggarrange(plt19,plt20,ncol = 2, nrow = 2)
print(plt21)
```
=======
#pca data set
pca_2022 <- prcomp(survey_data_2022_pca, scale = TRUE, center = TRUE)

#pca graph for variables
fviz_pca_var(pca_2022, select.var = list(contrib = 20), col.var = "contrib",
             gradient.cols = c("#eeaa46", "#797d97"), repel = TRUE)
```

## Informed Bar Plots 
>>>>>>> Stashed changes

